On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-07 Manuscript/reply.tex
comments on replies

% \jy{Spell check!}

\jy{For each comment, response first and at the end of each response,
  state what was done in the text. I usually don't quote text because
  if you make changes, you need to synchronize at two locations. Learn
  from the first version (which is a real reply letter for a paper).}
\mc{addressed}

\subsection*{Summary}

We thank the editor and the AE for the opportunity to revise the manuscript and
the two referees for their constructive comments. The manuscript has been
revised accordingly with the following notable changes:
\begin{enumerate}
\item Added clarifications of rationals for decisions regarding the experimental
design;
\item Reorganization of paragraphs on the Simulation Study, including moving the
Appendix on the Exponential Marginal Distribution Study to the main text;
\item Further discussion of the justification, advantages, and implications of
the Recentered Percentile CI;
\item Clarified wording and additional citations;
\item More detailed xxamination of limitations of study and block bootstrap 
in general
\item An Appendix on simulation study using block size 
$l = \lceil 2n^{1/3} \rceil$
\end{enumerate}

@@

Thank you for this suggestion. The motivation behind proposing such an interval 
was based on the 
simulation performance of the BC and BCA intervals, which will be discussed
further in the Results section. This has now been stated in the Recentered
Percentile CI pargarph.

@@

\jy{never use ``below'' because tables/figures are floats.}
\mc{addressed}

Thank you for this idea. We have provided Figure~\ref{fig:mu} as an 
example of what this suggested figure
would look like. 
\jy{1. Reduce the heights; put legend at the bottom; put the
  confidence intervals side by side for each sample size (see this
  paper for example plot:
  \url{https://iopscience.iop.org/article/10.1088/1748-9326/ac14ee/meta}.}
\mc{addressed}

@@

\jy{Left quote: `` (below the ESC key)}
\mc{addressed in reply and manuscript}

@@

Thank you for the comment. We expect the CIs that 
are based on bootstrap 
``tables" to depend on the 
asymptotic distribution of the statistics, but we expect such CIs to 
have similar performance for different error structures. For example, under the 
Central
Limit Theorem, we expect the asymptotic distribution of the sample mean to be 
approximately 
normal for both marginal normal distributions and marginal exponential 
distributions. Therefore, we do not expect CIs that are not based on bootstrap
``tables" (Percentile, BC, BCA, Recentered Percentile CI) to perform better 
under
non-normal error structures. We have called attention to this in the Exponential
Marginal Distribution subsection of the Design section.

@@

Thank you for the comment.  This terminology was used because 
\citet{efron1993introduction} refers to such CIs as 
``confidence intervals based on 
bootstrap `tables'." We have replaced all instances of the phrase 
``table-based bootstrap CIs" to ``confidence intervals based on bootstrap 
`tables'" for the sake of clarity.

@@

\eds{I don't think this answers the question.  The reviewer is saying that 0.95 
is close to the boundary of 1, so the undercoverage observed intervals
(especially when phi -0.4) may be due, at least in part, to the flaws 
of the asymptotic Wald interval you are using. 
\@ Jun: do you think he should try exact Clopper-Pearson
intervals for at least a few cases of undercoverage to verify it is not the Wald
interval that is causing the undercoverage, then comment on this in at least the
reply (and possibly also in the main paper)?}
\mc{plot\_norm\_mu\_1\_cup.pdf (exact Clopper-Pearson) seems to have about the same 
widths for high 
proportions
(especially for phi = -0.4) as {plot\_norm\_mu\_1.pdf} (Wald-Type)}
\jy{I thought the CP interval is for binomial proportions. How was it
  done here?}
\mc{this is the interval for the coverage rate, which is a proportion}

@@

\jy{No  need to duplicate the figures if they are already in the paper.}
\mc{addressed}

@@

Thank you for the suggestion. However, because of the deterioration for $\phi$, 
we found it hard to fix the limits on 
the 
y-axis without hurting the visualization for the other rows. 
Figure~\ref{fig:alt_phi1} is provided as an 
example:  \eds{refer to the Figure label, and avoid using `below' and `above'
terminology with latex because the figures are not always positioned as we may
have intended.}
\mc{addressed}

@@

@@

\eds{I only saw this citation in the abstract, not the discussion.  
Please remove this citation from the abstract and place in the discussion 
section where the sentence in question appears. In general,
try to avoid placing any citations in the abstract.}
\mc{addressed, sorry silly mistake}

@@

Thank you for the comment. We only
used serial dependences as strong as 0.4, because we only seek to 
establish the 
general trend as the strength of the autocorrelation 
increases, and how it varies depending on the sign of the autocorrelation and 
the parameter of interest. This justification has been added to the Design 
section.

@@

We are indebted to the reviewers for pointing out these vital discussion areas,
which have not only enriched the current paper but also charted a clear course
for our subsequent research endeavors.

>>>>

We thank the editor and the AE for the opportunity to revise the manuscript. and
the two referees for their constructive comments.
We are indebted to the reviewers for pointing out these vital discussion areas,
which have not only enriched the current paper but also charted a clear course
for our subsequent research endeavors.

The manuscript has been
revised accordingly with the following notable changes:
\jy{Be selective here for ``notable''. I'd not include items like `wording
  clarification'; your could put all the clarifications as one
  item. Keep this list short for the reviewers to have a  
  quick idea about the major changes (e.g., additional simulation studies).}

\begin{enumerate}
\item Added clarifications of rationals for decisions regarding the experimental
design;
\item Reorganization of paragraphs on the Simulation Study, including moving the
Appendix on the Exponential Marginal Distribution Study to the main text;
\item Further discussion of the justification, advantages, and implications of
the Recentered Percentile CI;
\item Clarified wording and additional citations;
\item More detailed xxamination of limitations of study and block bootstrap 
in general
\item An Appendix on simulation study using block size 
$l = \lceil 2n^{1/3} \rceil$
\end{enumerate}

@@

Thank you for this suggestion. The motivation behind the proposed
recentered CI is that. for the autocorrelation parameter in the
simulation studies, the centers of the existing CIs appeared to be a
biased estimator of the target while the spreadness of the CIs still
provide good uncertainty measures. This has now been added in the
Recentered Percentile CI pargarph.

@@

Thank you for this idea. We have provided Figure~\ref{fig:mu} as an 
example of what this suggested figure
would look like.

\jy{put the legend on one line.}

\jy{This plot seems fine to me. Could you make it for the other
  parameters too? Then we can make a decision. If we use this, the
  number of figures would be greatly reduced.}

@@

@@

Thank you for the comment. We expect the CIs that 
are based on bootstrap
\jy{Need to explain ``table'' methods better in the manuscript.}
``tables" to depend on the 
asymptotic distribution of the statistics, but we expect such CIs to 
have similar performance for different error structures. For example, under the 
Central
Limit Theorem, we expect the asymptotic distribution of the sample mean to be 
approximately 
normal for both marginal normal distributions and marginal exponential 
distributions. Therefore, we do not expect CIs that are not based on bootstrap
``tables" (Percentile, BC, BCA, Recentered Percentile CI) to perform better 
under
non-normal error structures. We have called attention to this in the Exponential
Marginal Distribution subsection of the Design section.

@@

Thank you for the comment.  This terminology was used because 
\citet{efron1993introduction} refers to such CIs as
\jy{This is still not clear. I think they mean CIs based on asymptotic
  distributions with estimated asymptotic variances. This is in
  contrast to percentile based CIs.}
``confidence intervals based on 
bootstrap `tables'." We have replaced all instances of the phrase 
``table-based bootstrap CIs" to ``confidence intervals based on bootstrap 
`tables'" for the sake of clarity.

@@

\eds{I don't think this answers the question.  The reviewer is saying that 0.95 
is close to the boundary of 1, so the undercoverage observed intervals
(especially when phi -0.4) may be due, at least in part, to the flaws 
of the asymptotic Wald interval you are using. 
\@ Jun: do you think he should try exact Clopper-Pearson
intervals for at least a few cases of undercoverage to verify it is not the Wald
interval that is causing the undercoverage, then comment on this in at least the
reply (and possibly also in the main paper)?}
\mc{plot\_norm\_mu\_1\_cup.pdf (exact Clopper-Pearson) seems to have about the same 
widths for high 
proportions
(especially for phi = -0.4) as {plot\_norm\_mu\_1.pdf} (Wald-Type)}

\jy{Are there big differences? We could report the CP CIs in the paper.}

@@

@@

Thank you for the suggestion. However, because of the deterioration for $\phi$, 
we found it hard to fix the limits on the 
y-axis without hurting the visualization for the other rows. 
Figure~\ref{fig:alt_phi1} is provided as an example:

@@

\jy{I'm interested in seeing the figures overlaid as in
  Figure~\ref{fig:mu}.}

@@

@@

Thank you for the comment. We only
used serial dependences as strong as 0.4, because we only seek to 
establish the 
general trend as the strength of the autocorrelation 
increases, and how it varies depending on the sign of the autocorrelation and 
the parameter of interest. This justification has been added to the Design 
section. \jy{Add a comment in the discussion about what'd be expected
  with higher dependence levels.}

@@
